---
title: "Third Data Viz"
description: |
  In this last visualization, I want to provide information about the average of risky choices made by the girls in the sample, differentiating when the risky choices were made in gain trials or loss trials of the CUPS task. Visit the About section for a brief description of the task. 
author:
  - name: Alejandra Garcia Isaza
    url: https://github.com/Alegarisa
date: 03-18-2019
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)


library(tidyverse)
library(rio)
library(here)
library(dplyr)
library(gghighlight)
library(patchwork)
library(gganimate)
library(ggplot2)
library(gifski)
library(colorblindr)

theme_set(theme_minimal(base_size = 15))

```

```{r}

d <- import(here("data", "alejandra-sim.csv"), setclass = "tbl_df") 

# editing names
d <- rename(d, treatment = c("group"), agew1 = c("md1age"), agew8 = c("md8age"), maltxrecs = c("total_number_maltx_records"), placechange = c("pre_b_lplacechanges"), severitymaltx = c("severitymn"), totcupsgain = c("cup_agrto"), totcupsloss = c("cup_alrto"))

```

In the first version of this visualization, I just tidied the data to get the total number of risky choices made in loss and gain domains in one column, but it didn't work. I realized that I had to take the averages next.  

```{r, fig.height= 6, fig.width=8}

tidy_d2 <- d %>%
  gather(valence, number, 22:23)

tidy_d2 <- tidy_d2 %>%
  mutate(valence = factor(valence),
         family = factor(family))


ggplot(tidy_d2, aes(valence, number)) +
  geom_col() +
  facet_wrap(~ treatment)

```

In the second attempt, I took the averages of the risky choices made in each of the domains, but still. the Y-axis was not showing the average but a count. 

```{r, fig.height= 6, fig.width=8}

d2 <- d %>%
  select(family, treatment, totcupsgain, totcupsloss) %>%
  group_by(treatment) %>%
  mutate(`Seek gains` = mean(totcupsgain, na.rm = TRUE),
         `Avoid losses` = mean(totcupsloss, na.rm = TRUE))

d2 <- d2 %>%
  gather(domain, avg, -1:-4)

ggplot(d2, aes(domain, avg)) +
  geom_col(fill = "cornflowerblue") + # I don't know why the y-axis goes until 750 if I already calculated the averages.
  facet_wrap(~ treatment) + 
  labs(title = "Average of Risky Choices made to Seek Gains and To avoid Losses by Treatment Condition",
       subtitle = "Decision Making Assessed with CUPS Task",
       y = "Average of Risky Choices",
       x = "")

```

For the third and final version of this visualization, I decided to abort the mission of doing a dynamite plot, which I finally understood is not very effective and may be deceiving, and went for a dot plot.  In this visualization, you can appreciate the spread of the data points, where clusters of data are, and you can still add the average (the gray dots) and errors bars. I felt happy about the result of this visualization! 

```{r, fig.height= 6, fig.width=8}

tidy_d2 <- tidy_d2 %>%
  mutate(valence = fct_recode(valence,
                           "Avoid losses" = "totcupsloss", # TOTAL OF RISKY CHOICES MADE IN LOSS DOMAIN
                           "Seek gains" = "totcupsgain")) # TOTAL OF RISKY CHOICES MADE IN GAIN DOMAIN

ggplot(tidy_d2, aes(valence, number)) +
  geom_point(position = position_jitter(0.3), alpha = 0.4, color = "cornflowerblue", size = 3) + 
  stat_summary(fun.y = mean, geom = "point", color = "gray30", size = 3) +
  stat_summary(fun.data = mean_sdl, geom = "errorbar", width = 0.2, col = "gray60") +
  facet_wrap(~ treatment) + 
  scale_y_continuous("Average of Risky Choices", limits = c(0, 40)) +
  labs(title = "Average of Risky Choices Made to Seek Gains/Avoid Losses",
       subtitle = "Decision Making Assessed with CUPS Task",
       x = "") +
  theme(plot.title = element_text(family = "sans", size = 16, face = "bold", hjust = 0), 
        plot.subtitle = element_text(family = "sans", size = 14, face = "italic", hjust = 0,
                                     margin = margin(0, 0, 30, 0)),
        axis.text.x.bottom = element_text(family = "sans", size = 12),
        axis.title.y = element_text(family = "sans", size = 12, margin = margin(20, 20, 10, 10)))

```






